Happiness versus Income Awareness

### 2022-02-28 outputs/paper/Paper2 final.Rmd
finalfinal

---
title: "Happiness versus Income Awareness"
subtitle: "Will people be happier if they know each other's income?"
author: 
  - Xiao Bai
  - Yichun Zhang
date: "27/02/2022"
output:
  pdf_document:
    toc: true
    toc_depth: 2
abstract: "In 2001, tax records in Norwey becaome easily accessible online, which allows everyone to see their income level and make comparsion with other people's income. The populatiry of searching the word 'Skattelister' (tax record list) has increased significantly since the introduction of tax data in 2001. People has large interest in the tax lists: for every five searches for YouTube, there was about one for skattelister. However, the introduction of this tax record list would cause a negative effect on the public as the income comparision model reports that the visible income transparency can exntend the disparity in well-being between groups of people with higher and lower income. "
bibliography: references.bib
---

>>>>

---
title: "Happiness versus Income Awareness"
subtitle: "Will people be happier if they know each other's income?"
author: 
  - Xiao Bai
  - Yichun Zhangah
date: "27/02/2022"
output:
  pdf_document:
    toc: true
    toc_depth: 2
abstract: "In 2001, tax records in Norwey becaome easily accessible online, which allows everyone to see their income level and make comparsion with other people's income. The populatiry of searching the word 'Skattelister' (tax record list) has increased significantly since the introduction of tax data in 2001. People has large interest in the tax lists: for every five searches for YouTube, there was about one for skattelister. However, the introduction of this tax record list would cause a negative effect on the public as the income comparision model reports that the visible income transparency can exntend the disparity in well-being between groups of people with higher and lower income. "
bibliography: references.bib
---
